\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-28 Writeup/paper.tex
Minor improvements to related work section

\section{Related Work}\label{sec:related}
% Relevant work that has been done
There have been a number of studies on how the performance of video streaming affects the quality of experience (QoE) for the user. Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 months worth of YouTube packet flows from a large European ISP. The study challenges Google's Video Quality Report \footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}. Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction for in QoE for many YouTube users. Fiadino \textit{et al.} \cite{6932930} developed an tool for ISP's to detect unexpected cache-selection events and changes in the traffic delivered by CDNs. As such, anomalous CDN behaviour can have a large impact for ISP's carrying the traffic and end-users \cite{6932930, Plissonneau:2012:LVH:2155555.2155588}. Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDN's to diagnose large latency increases on the network through passive measurement of traffic and routing. Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with interdomain routing changes and more than one-third involve a shift in traffic to different servers. Juluri \textit{et al.} \cite{6038496} developed a tool to measure playback quality on an end-host. The tool captures various metrics such as delay towards the server, download
rates, and buffering duration \cite{6038496}. These can then be used to measure Quality of Experience.

In 2007 Gill \textit{et al.} \cite{Gill:2007:YTC:1298306.1298310} studied the usage patterns, file properties, popularity and transfer behaviour of YouTube. Its findings found that caching could be used effectively to scale Web 2.0 applications such as YouTube \cite{Gill:2007:YTC:1298306.1298310}.In 2011, Torres \textit{et al.} \cite{5961681} analysed a week-long dataset collected from the edge of five networks. The study determined the location of YouTube servers and revealed that round trip time (RTT) is not the only factor determining video server selection \cite{5961681}. Other factors that were found to affect server selection were load-balancing, the DNS server used and popularity of the accessed video \cite{5961681}.

Labovitz \textit{et al.} \cite{Labovitz:2010:IIT:2043164.1851194} analysed 2 years worth of internet traffic through 110 different cable operators, international transit backbones, regional networks and content providers. The study found that there was a significant rise in video traffic and that the majority of inter-domain traffic flows directly between large content providers, CDNs and consumer networks.

@@

\section{Results}\label{sec:results}
\subsection{Home network}
% TODO (Brian) Maybe run a speed test so we can quote the results and give perspective for our result numbers?

@@

\begin{table}
	\caption{Averaged throughput (KB/s) across ISPs}
	\label{avgThroughputAcrossISP}
	\makebox[\linewidth]{
	\small
	\begin{tabular}{|l|l|c|c|c|} \hline
	Run & Source & Content \\ \hline
	1 & Unpopular Youtube & 197.8 \\ \hline
	  & Popular Youtube   & 202.6 \\ \hline
	  & Soundcloud        & 197.9 \\ \hline
	  & Twitch.tv         & 201.2 \\ \hline
	2 & Unpopular Youtube & 201.9 \\ \hline
	  & Popular Youtube   & 197.8 \\ \hline
	  & Soundcloud        & 201.3 \\ \hline
	  & Twitch.tv         & 203.1 \\ \hline
	3 & Unpopular Youtube & 202.8 \\ \hline
	  & Popular Youtube   & 200.4 \\ \hline
	  & Soundcloud        & 203.6 \\ \hline
	  & Twitch.tv         & 204.9 \\ \hline
	\end{tabular}}
\end{table}
It is immediately clear that the throughput does not differ much across websites or runs, although this is not unexpected given the relatively low bandwidth of the home connection. Another trend which is immediately clear is the significant difference between ping and number of hops to Youtube and Soundcloud/Twitch.tv. This is simply because Youtube content is cached within South Africa while Twitch.tv and Soundcloud do not, most likely because they are not large enough to be able to afford setting up expensive caches all over the world.

@@

\begin{table}
	\caption{Offset from median throughput (KB/s, higher is better)}
	\label{table:OffsetFromMedianThroughput}
	\makebox[75mm]{
	\small
	\begin{tabular}{|l|c|c|c|c|c|} \hline
	 & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
	\small{Unpopular YT} & 1.5  & -0.5  & 2.1   & -3.9 & -2.9 \\ \hline
	Popular YT           & -0.8 & -8.5  & -3.1  & 0.4  & -1.2 \\ \hline
	Soundcloud           & 0.1  & -5.1  & -1.3  & 2.5  & -5.4 \\ \hline
	Twitch.tv            & -0.4 & 0.3   & -6.8  & 0.7  & -0.6 \\ \hline
	Total                & 0.4  & -13.8 & -9.2  & -0.3 & -10.2\\ \hline
	\end{tabular}}
\end{table}
While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping than other ISPs. The only exception to this is the ping to the Youtube website where WebAfrica performed slightly better than the median.

The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.

\subsubsection{Content server owners}
Although not shown in the tables, it is worth noting the results of the WHOIS lookup for the IPs that served the content. In the case of Youtube, which server provides the content depends on which networks make use of which local caches as well as whether or not the requested content is available in the cache. This is expected as Youtube is a very popular source of content and ISPs setup complex caching systems to reduce bandwidth. For Soundcloud and Twitch.tv however, this is not the case. All Soundcloud content gets delivered from a IP address that is registered to Amazon, suggesting that Soundcloud uses Amazon Web Services for all of its content storage and distribution. The content servers for Twitch.tv are not as consistent. While Afrihost, Telkom and WebAfrica all receive Twitch content from an IP registered to ``MCI Communications Services'' (the same company that is the registered owner of the CDN that hosts the content), Axxess and Cybersmart do not. Axxess routes to a CDN owned by MCI, but the actual content comes from a server owned by ``Akamai International''. Cybersmart does not even receive Twitch content from the same server each time, content arrives from serves that are owned by a variety of other companies.

@@

Note that some of the throughput data points are missing, this is because we measure throughput as youtube-dl downloads and in those cases the download finished before we could get a good measure.
\subsubsection{Test case 1}
The first test case used the following media URLs:
\begin{itemize}
	\item Unpopular Youtube video: \\ 
	https://www.youtube.com/watch?v=yRfwRsJrMzI
	\item Popular Youtube video: \\
	https://www.youtube.com/watch?v=9bZkp7q19f0
	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
\end{itemize}
Table \ref{table:UCTPingTests-TestCase1}, \ref{table:UCTHopCount-TestCase1} and \ref{table:UCTThroughput-TestCase1} contain the ping, number of hops and throughput for each run of test case 1.

\begin{table}
    \centering
    \caption{Ping using UCT network - Test 1}
    \label{table:UCTPingTests-TestCase1}
    \makebox[\linewidth]{
    \small
    \begin{tabular}{|l|l|c|c|c|} \hline
    Run & Source & Website & CDN & Content \\ \hline
    1 & Unpopular Youtube & 19  & 18  & 184 \\ \hline
      & Popular Youtube   & 18  & 18  & 18  \\ \hline
      & Twitch.tv         & 148 & 148 & 148 \\ \hline
      & Soundcloud        & 148 & 149 & 149 \\ \hline
    2 & Unpopular Youtube & 19  & 18  & 18  \\ \hline
      & Popular Youtube   & 19  & 18  & 19  \\ \hline
      & Twitch.tv         & 148 & 150 & 153 \\ \hline
      & Soundcloud        & 148 & 148 & 192 \\ \hline
    3 & Unpopular Youtube & 19  & 19  & 18  \\ \hline
      & Popular Youtube   & 19  & 18  & 18  \\ \hline
      & Twitch.tv         & 148 & 152 & 148 \\ \hline
      & Soundcloud        & 148 & 149 & 150 \\ \hline
    \end{tabular}}
\end{table}

\begin{table}
	\centering
	\caption{Hop count using UCT network - Test 1}
	\label{table:UCTHopCount-TestCase1}
	\makebox[\linewidth]{
	\small
    \begin{tabular}{|l|l|c|c|c|} \hline
    Run & Source & Website & CDN & Content \\ \hline
    1 & Unpopular Youtube & 9 & 9 & 16 \\ \hline
      & Popular Youtube   & 9 & 9 & 9 \\ \hline
      & Twitch.tv         & 13 & 11 & 11 \\ \hline
      & Soundcloud        & 11 & 18 & 18 \\ \hline
    2 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
      & Popular Youtube   & 10 & 9 & 9 \\ \hline
      & Twitch.tv         & 12 & 13 & 13 \\ \hline
      & Soundcloud        & 11 & 17 & 17 \\ \hline
    3 & Unpopular Youtube & 10 & 9 & 9 \\ \hline
      & Popular Youtube   & 9 & 9 & 9 \\ \hline
      & Twitch.tv         & 13 & 13 & 13 \\ \hline
      & Soundcloud        & 11 & 18 & 18 \\ \hline
    \end{tabular}}
\end{table}

\begin{table}
	\centering
	\caption{Throughput using UCT network - Test 1}
	\label{table:UCTThroughput-TestCase1}
	\makebox[\linewidth]{
	\small
    \begin{tabular}{|l|l|c|c|c|} \hline
    Run & Source & Content    \\ \hline
    1 & Unpopular Youtube & 521.5  \\ \hline
      & Popular Youtube   & 9809.9 \\ \hline
      & Twitch.tv         & 11366.4    \\ \hline
      & Soundcloud        & -    \\ \hline
    2 & Unpopular Youtube & 6481.9  \\ \hline
      & Popular Youtube   & 9840.6  \\ \hline
      & Twitch.tv         & 3440.6    \\ \hline
      & Soundcloud        & -    \\ \hline
    3 & Unpopular Youtube & 8069.1  \\ \hline
      & Popular Youtube   & 9881.6 \\ \hline
      & Twitch.tv         & 11335.7    \\ \hline
      & Soundcloud        & -    \\ \hline
    \end{tabular}}
\end{table}

\subsubsection{Test case 2}
The second test case used the following media URLs:
\begin{itemize}
	\item Unpopular Youtube video: \\ 
	https://www.youtube.com/watch?v=tSzaFuCxjs0
	\item Popular Youtube video: \\
	https://www.youtube.com/watch?v=9bZkp7q19f0
	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
\end{itemize}
Table \ref{table:UCTPing-TestCase2}, \ref{table:UCTHopCount-TestCase2} and \ref{table:UCTThroughput-TestCase2} contain the ping, number of hops and throughput for run of test case 2.

\begin{table}
	\centering
	\caption{Ping using UCT network - Test 2}
	\label{table:UCTPing-TestCase2}
	\makebox[\linewidth]{
	\small
    \begin{tabular}{|l|l|c|c|c|} \hline
    Run & Source & Website & CDN & Content \\ \hline
    1 & Unpopular Youtube & 19 & 3 & 182  \\ \hline
      & Popular Youtube   & 19 & 18 & 18  \\ \hline
      & Twitch.tv         & 148 & 150 & 148  \\ \hline
      & Soundcloud        & 148 & 148 & 148  \\ \hline
    2 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
      & Popular Youtube   & 19 & 18 & 18  \\ \hline
      & Twitch.tv         & 148 & 150 & 150  \\ \hline
      & Soundcloud        & 148 & 148 & 148  \\ \hline
    3 & Unpopular Youtube & 19 & 3 & 3  \\ \hline
      & Popular Youtube   & 20 & 18 & 18 \\ \hline
      & Twitch.tv         & 148 & 148 & 148  \\ \hline
      & Soundcloud        & 148 & 149 & 148  \\ \hline
    \end{tabular}}	
\end{table}

\begin{table}
	\centering
	\caption{Hop count using UCT network - Test 2}
	\label{table:UCTHopCount-TestCase2}
	\makebox[\linewidth]{
	\small
    \begin{tabular}{|l|l|c|c|c|} \hline
    Run & Source & Website & CDN & Content \\ \hline
    1 & Unpopular Youtube & 9 & 7 & 16  \\ \hline
      & Popular Youtube   & 10 & 9 & 9  \\ \hline
      & Twitch.tv         & 12 & 13 & 13  \\ \hline
      & Soundcloud        & 11 & 17 & 17  \\ \hline
    2 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
      & Popular Youtube   & 9 & 9 & 9  \\ \hline
      & Twitch.tv         & 13 & 13 & 13  \\ \hline
      & Soundcloud        & 11 & 16 & 16  \\ \hline
    3 & Unpopular Youtube & 10 & 7 & 7  \\ \hline
      & Popular Youtube   & 9 & 9 & 9  \\ \hline
      & Twitch.tv         & 12 & 12 & 12  \\ \hline
      & Soundcloud        & 11 & 18 & 18  \\ \hline
    \end{tabular}}
\end{table}

\begin{table}
	\centering
	\caption{Throughput using UCT network - Test 2}
	\label{table:UCTThroughput-TestCase2}
	\makebox[\linewidth]{
	\small
    \begin{tabular}{|l|l|c|c|c|} \hline
    Run & Source & Content    \\ \hline
    1 & Unpopular Youtube & 1525.8 \\ \hline
      & Popular Youtube   & 9799.7 \\ \hline
      & Twitch.tv         & 11427.8 \\ \hline
      & Soundcloud        & - \\ \hline
    2 & Unpopular Youtube & 4331.5 \\ \hline
      & Popular Youtube   & 9820.2 \\ \hline
      & Twitch.tv         & 11397.1 \\ \hline
      & Soundcloud        & - \\ \hline
    3 & Unpopular Youtube & 11274.2 \\ \hline
      & Popular Youtube   & 9175.0 \\ \hline
      & Twitch.tv         & 11325.4 \\ \hline
      & Soundcloud        & 1689.6 \\ \hline
    \end{tabular}}
\end{table}

\subsubsection{Discussions}
Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced. Note the difference in throughput for the unpopular Youtube video on the first run to the second and third runs. On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a bitrate far below what the connection supports. On the run 2 the video has been cached and is delivered with a significantly higher throughput. What is interesting to note however, is that on run 3 the throughput is again significantly higher than run 2, even though the ping to the server that delivers it has not changed. This suggests that the cache considers it to be "hotter" because of the additional request for it, and serves it at a higher throughput.

Another interesting point to make is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos. This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular Youtube content is being delivered from caches within Cape Town.

>>>>

\section{Related Work}\label{sec:related}
% Relevant work that has been done
There have been a number of studies on how the performance of video streaming affects the quality of experience (QoE) for the user. Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 months worth of YouTube packet flows from a large European ISP. The study challenges Google's Video Quality Report\footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}. Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction for in QoE for many YouTube users. Fiadino \textit{et al.} \cite{6932930} developed an tool for ISP's to detect unexpected cache-selection events and changes in the traffic delivered by CDNs. Anomalous CDN behaviour has been shown to have a large impact for ISP's carrying the traffic and end-users \cite{6932930, Plissonneau:2012:LVH:2155555.2155588}. Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDN's to diagnose large latency increases on the network through passive measurement of traffic and routing. Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with interdomain routing changes and more than one-third involve a shift in traffic to different servers. Juluri \textit{et al.} \cite{6038496} developed Pytomo, a tool to measure playback quality on an end-host. The tool captures various metrics such as delay towards the server, download rates and buffering duration \cite{6038496}. These can then be used to measure Quality of Experience.

In 2007 Gill \textit{et al.} \cite{Gill:2007:YTC:1298306.1298310} studied the usage patterns, file properties, popularity and transfer behaviour of YouTube. Its findings found that caching could be used effectively to scale Web 2.0 applications such as YouTube \cite{Gill:2007:YTC:1298306.1298310}. In 2011, Torres \textit{et al.} \cite{5961681} analysed a week-long dataset collected from the edge of five networks. The study determined the location of YouTube servers and revealed that round trip time (RTT) is not the only factor determining video server selection \cite{5961681}. Other factors that were found to affect server selection were load-balancing, the DNS server used and popularity of the accessed video \cite{5961681}.

Labovitz \textit{et al.} \cite{Labovitz:2010:IIT:2043164.1851194} analysed 2 years worth of internet traffic through 110 different cable operators, international transit backbones, regional networks and content providers. The study found that there was a significant rise in video traffic \cite{Labovitz:2010:IIT:2043164.1851194}. It also found that the majority of inter-domain traffic flows between large content providers, CDNs and consumer networks \cite{Labovitz:2010:IIT:2043164.1851194}.

@@

\section{Results}\label{sec:results}
\subsection{Home network}
%TODO (Jacques) I think it might be good to analyse the WHOIS organisation for Twitch and Soundcloud. Is the same organisation serving up the content for each ISP? Who is serving up the content for these two services?

% TODO (Brian) Maybe run a speed test so we can quote the results and give perspective for our result numbers?

@@

\begin{table}
	\caption{Averaged throughput (KB/s) across ISPs}
	\label{avgThroughputAcrossISP}
	\makebox[\linewidth]{
	\small
	\begin{tabular}{|l|l|c|c|c|} \hline
	Run & Source & Content \\ \hline
	1 & Unpopular Youtube & 197.8 \\ \hline
	  & Popular Youtube   & 202.6 \\ \hline
	  & Soundcloud        & 197.9 \\ \hline
	  & Twitch.tv         & 201.2 \\ \hline
	2 & Unpopular Youtube & 201.9 \\ \hline
	  & Popular Youtube   & 197.8 \\ \hline
	  & Soundcloud        & 201.3 \\ \hline
	  & Twitch.tv         & 203.1 \\ \hline
	3 & Unpopular Youtube & 202.8 \\ \hline
	  & Popular Youtube   & 200.4 \\ \hline
	  & Soundcloud        & 203.6 \\ \hline
	  & Twitch.tv         & 204.9 \\ \hline
	\end{tabular}}
\end{table}
% TODO: Table of "offset from median" of the metrics for each ISP
It is immediately clear that the throughput does not differ much across websites or runs, although this is not unexpected given the relatively low bandwidth of the home connection. Another trend which is immediately clear is the significant difference between ping and number of hops to Youtube and Soundcloud/Twitch.tv. This is simply because Youtube content is cached within South Africa while Twitch.tv and Soundcloud do not, most likely because they are not large enough to be able to afford setting up expensive caches all over the world.

@@

\begin{table}
	\caption{Offset from median throughput (KB/s, higher is better)}
	\label{table:OffsetFromMedianThroughput}
	\makebox[75mm]{
	\small
	\begin{tabular}{|l|c|c|c|c|c|} \hline
	 & \small{Afrihost} & \small{Axxess} & \small{Cybersmart} & \small{Telkom} & \small{WebAfrica} \\ \hline
	\small{Unpopular YT} & 1.5  & -0.5  & 2.1   & -3.9 & -2.9 \\ \hline
	Popular YT           & -0.8 & -8.5  & -3.1  & 0.4  & -1.2 \\ \hline
	Soundcloud           & 0.1  & -5.1  & -1.3  & 2.5  & -5.4 \\ \hline
	Twitch.tv            & -0.4 & 0.3   & -6.8  & 0.7  & -0.6 \\ \hline
	Total                & 0.4  & -13.8 & -9.2  & -0.3 & -10.2\\ \hline
	\end{tabular}}
\end{table}
While the different ISPs clearly perform differently, the only significant trend is that WebAfrica consistently gave a higher ping, although still less than 100ms, suggesting that the caches for WebAfrica are still within South Africa but not in Cape Town (for example, they could be in Johannesburg). 
% Can you expand the above statement. What is less than 100ms? Because twitch and soundcloud is always in EU > 100ms.
The differences in throughput are not significant and while there are some significant differences in latency, they are not consistent and so are likely due to external factors on the network.

@@

Note that some of the throughput data points are missing, this is because we measure throughput as youtube-dl downloads and in those cases the download finished before we could get a good measure.
\subsubsection{Test case 1}
The first test case used the following media URLs:
\begin{itemize}
	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
\end{itemize}
Table \ref{table:UCTPingTests-TestCase1}, \ref{table:UCTHopCount-TestCase1} and \ref{table:UCTThroughput-TestCase1} contain the ping, number of hops and throughput for each run of test case 1.

\begin{table}
	\centering
	\caption{Ping using UCT network}
	\label{table:UCTPingTests-TestCase1}
	\makebox[\linewidth]{
	\small
	\begin{tabular}{|l|l|c|c|c|} \hline
	Run & Source & Website & CDN & Content \\ \hline
	1 & Unpopular Youtube & 18  & 49  & 44  \\ \hline
	  & Popular Youtube   & 45  & 19  & 18  \\ \hline
	  & Soundcloud        & 179 & 148 & 154 \\ \hline
	  & Twitch.tv         & 148 & 155 & 148 \\ \hline
	2 & Unpopular Youtube & 21  & 19  & 19  \\ \hline
	  & Popular Youtube   & 19  & 26  & 19  \\ \hline
	  & Soundcloud        & 148 & 149 & 148 \\ \hline
	  & Twitch.tv         & 148 & 148 & 148 \\ \hline
	3 & Unpopular Youtube & 3   & 19  & 19  \\ \hline
	  & Popular Youtube   & 2   & 45  & 68  \\ \hline
	  & Soundcloud        & 148 & 148 & 148 \\ \hline
	  & Twitch.tv         & 151 & 154 & 148 \\ \hline
	\end{tabular}}
\end{table}

\begin{table}
	\centering
	\caption{Hop count using UCT network}
	\label{table:UCTHopCount-TestCase1}
	\makebox[\linewidth]{
	\small
	\begin{tabular}{|l|l|c|c|c|} \hline
	Run & Source & Website & CDN & Content \\ \hline
	1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
	  & Soundcloud        & 9 & 9 & 9 \\ \hline
	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
	2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
	  & Soundcloud        & 9 & 9 & 9 \\ \hline
	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
	3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
	  & Soundcloud        & 9 & 9 & 9 \\ \hline
	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
	\end{tabular}}
\end{table}

\begin{table}
	\centering
	\caption{Throughput using UCT network}
	\label{table:UCTThroughput-TestCase1}
	\makebox[\linewidth]{
	\small
	\begin{tabular}{|l|l|c|c|c|} \hline
	Run & Source & Content \\ \hline
	1 & Unpopular Youtube & 1484.8  \\ \hline
	  & Popular Youtube   & 8560.6  \\ \hline
	  & Soundcloud        & 1351.7  \\ \hline
	  & Twitch.tv         & 11284.5 \\ \hline
	2 & Unpopular Youtube & 7690.2  \\ \hline
	  & Popular Youtube   & 8161.3  \\ \hline
	  & Soundcloud        & -       \\ \hline
	  & Twitch.tv         & 11264.0 \\ \hline
	3 & Unpopular Youtube & 7598.1  \\ \hline
	  & Popular Youtube   & 9543.7  \\ \hline
	  & Soundcloud        & -       \\ \hline  
	  & Twitch.tv         & 11233.3 \\ \hline
	\end{tabular}}
\end{table}

\subsubsection{Test case 2}
The second test case used the following media URLs:
\begin{itemize}
	\item Unpopular Youtube video: \\ https://www.youtube.com/watch?v=nKETYT-2NY8
	\item Popular Youtube video: \\ https://www.youtube.com/watch?v=9bZkp7q19f0
	\item Soundcloud audio: \\ https://soundcloud.com/nocopyrightsounds/lensko-cetus-ncs-release
	\item Twitch.tv video: \\ https://www.twitch.tv/dota2ti/v/83400929
\end{itemize}
Table \ref{table:UCTPing-TestCase2}, \ref{table:UCTHopCount-TestCase2} and \ref{table:UCTThroughput-TestCase2} contain the ping, number of hops and throughput for run of test case 2.

\begin{table}
	\centering
	\caption{Ping using UCT network}
	\label{table:UCTPing-TestCase2}
	\makebox[\linewidth]{
	\small
	\begin{tabular}{|l|l|c|c|c|} \hline
	Run & Source & Website & CDN & Content \\ \hline
	1 & Unpopular Youtube & 4   & 19  & 188 \\ \hline
	  & Popular Youtube   & 4   & 19  & 21  \\ \hline
	  & Twitch.tv         & 148 & 154 & 148 \\ \hline
	  & Soundcloud        & 148 & 148 & 0   \\ \hline
	2 & Unpopular Youtube & 3   & 47  & 19  \\ \hline
	  & Popular Youtube   & 4   & 20  & 19  \\ \hline
	  & Twitch.tv         & 172 & 154 & 0   \\ \hline
	  & Soundcloud        & 148 & 149 & 149 \\ \hline
	3 & Unpopular Youtube & 4   & 33  & 19  \\ \hline
	  & Popular Youtube   & 3   & 20  & 18  \\ \hline
	  & Twitch.tv         & 149 & 148 & 0   \\ \hline
	  & Soundcloud        & 148 & 148 & 148 \\ \hline
	\end{tabular}}
\end{table}

\begin{table}
	\centering
	\caption{Hop count using UCT network}
	\label{table:UCTHopCount-TestCase2}
	\makebox[\linewidth]{
	\small
	% TODO: Update these with correct values
	\begin{tabular}{|l|l|c|c|c|} \hline
	Run & Source & Website & CDN & Content \\ \hline
	1 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
	  & Soundcloud        & 9 & 9 & 1 \\ \hline
	2 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
	  & Soundcloud        & 9 & 9 & 1 \\ \hline
	3 & Unpopular Youtube & 9 & 9 & 9 \\ \hline
	  & Popular Youtube   & 9 & 9 & 9 \\ \hline
	  & Twitch.tv         & 9 & 9 & 9 \\ \hline
	  & Soundcloud        & 9 & 9 & 1 \\ \hline
	\end{tabular}}
\end{table}

\begin{table}
	\centering
	\caption{Throughput using UCT network}
	\label{table:UCTThroughput-TestCase2}
	\makebox[\linewidth]{
	\small
	\begin{tabular}{|l|l|c|c|c|} \hline
	Run & Source & Content \\ \hline
	1 & Unpopular Youtube & 190.9   \\ \hline
	  & Popular Youtube   & 8048.6  \\ \hline
	  & Twitch.tv         & 10526.7 \\ \hline
	  & Soundcloud        & 1341.4  \\ \hline
	2 & Unpopular Youtube & 9513.0  \\ \hline
	  & Popular Youtube   & 8335.4  \\ \hline
	  & Twitch.tv         & 11397.1 \\ \hline
	  & Soundcloud        & -       \\ \hline
	3 & Unpopular Youtube & 9840.6  \\ \hline
	  & Popular Youtube   & 7260.2  \\ \hline
	  & Twitch.tv         & 11274.2 \\ \hline  
	  & Soundcloud        & -       \\ \hline
	\end{tabular}}
\end{table}

\subsubsection{Discussions}
Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced. The Youtube web page  gets served at a much lower ping than the actual content, suggesting that the web page is being cached within UCT's network. Also note the difference in throughput for the unpopular Youtube video on the first run to the other runs. On run 1 the video is not cached (as is evident by the higher ping) and is delivered at a far lower throughput than on subsequent or than the popular Youtube video.

Another point of particular interest is the very low ping and hop counts that appear in test case 2. The results show the test machine's IP as the IP that the content was being retrieved from. This is most likely a bug in our tool's parsing of tcpdump's output.
